---
title: "Lecture 3 in-class data wrangling, munging and creating tidy datasets"
subtitle: "Sep 9, 2020"
author: "Robert Settlage"
authorbox: false
slug: "Lecture-2-inclass"
date: 2020-08-22
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: inline 
---

# Quick review

# summary functions
1. what does the imported data look like?  Missing values, odd structures?
2. What summaries, text or plots, might you make on the girder data as imported assuming 9 different girders? 

# dplyr
1. Using dplyr functions, can you summarize the data? Mean by method, mean by girder?  Min? Max?
```{r}
library(dplyr)
library(tidyr)
iris %>% 
    group_by(Species) %>%
    summarize(avg=mean(Sepal.Width)) 
```

# homework practice and expectations

Girder experiment
<https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/fullgirder.dat>
```{r}
# look at first few lines
# what strategy should we use
# what summaries/plots are informative
# 
```


## homework 2
